A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-11-01 response.tex

\textit{Thanks a lot for the information and clarification in the rebuttal and the new paper version. I would suggest the authors make the following changes in the next paper version.}

\subsection{More discussion on the size and type of the patches}

\textit{\textbf{R2:} Inspired by the last paragraph of Section 4.1, can authors discuss which of the following is more important for Rust in the next paper version: fixing bugs and fixing compilation errors?}

\vspace*{1em} \noindent \textbf{Response:} Added more discussion regarding this to the last paragraph of Section 4.1. We discuss that we consider bugs as potentially more critical, because an unresolved bug can remain dormant within the system and unintentionally get deployed, whereas a program with compilation errors cannot be shipped by developers.

@@

\vspace*{1em} \noindent \textbf{Response:} \todo{Probably just do what he asks.}

\subsection{Paraphrasing and providing clearer explanation}

\textit{\textbf{R2:} In Section 2.3.2, the authors use sentences from an existing paper directly (although quotes are added). I don't think this is a good way to write an academic paper. Please paraphrase these sentences.}

\vspace*{1em} \noindent \textbf{Response:} Paraphrased the three definition that were directly quoted.

### 2023-11-01 discussion.tex
two todos from reviewer 2 resolved

Conversely, we were surprised to find that Ruxanne reported no patterns associated with certain Rust-related features. For instance, we did not observe any patterns associated with the Rust \verb+move+ operator, which has been known to plague many beginning Rust programmers. \verb+move+ is used to transfer the ownership of values to a closure. In some cases (e.g. multithreading), not moving the ownership could create invalid references. Rust compiler checks prevent such errors. Our speculation is that, since Rust enforces strict compiler checks, programmers usually get many compile-time errors, but they only push their code once it is free of compile errors. We thus would not observe patterns which do not make it to the repository.

>>>>

Conversely, we were surprised to find that Ruxanne reported no patterns associated with certain Rust-related features. For instance, we did not observe any patterns associated with the Rust \verb+move+ operator, which has been known to plague many beginning Rust programmers. \verb+move+ is used to transfer the ownership of values to a closure. In some cases (e.g. multithreading), not moving the ownership could create invalid references. Rust compiler checks prevent such errors. Our speculation is that, since Rust enforces strict compiler checks, programmers usually get many compile-time errors, but they only push their code once it is free of compile errors. We thus would not observe patterns which do not make it to the repository. While comparing the importance of bugs and compilation errors can be challenging, we tend to consider bugs as potentially more critical. This is because a bug, if left unresolved, can remain dormant within the system and inadvertently get deployed, whereas a program with compilation errors cannot be shipped by developers.

### 2023-11-01 methodology.tex
two todos from reviewer 2 resolved

\begin{itemize}
    \item bug-fix: ``The changed code actually fixes the behavior of software, which can represent fixes for a bug type''. We include here changes that improve program performance, as they fix the behaviour of the software.

    \item fix-induced: ``The changed code is a group of bug-fixing code changes but not representing an actual bug fix, e.g., adding new input parameters to a method, the method signature and method call must be changed correspondingly''.

    \item refactoring: ``the changed code does not modify the software behavior, e.g., for better readability or encapsulation''.
\end{itemize}

>>>>

\begin{itemize}
    \item bug-fix: The code change rectifies the undesired behavior in the software system, providing fixes for a specific bug type. We also include here changes that improve program performance, as they fix the behaviour of the software.

    \item fix-induced: The code change is a part of a bug-fixing code and does not constitute the whole bug fix. For instance, introducing additional input parameters to a method also requires adjustments in the corresponding method invocations and does not represent the complete bug fix on its own.

    \item refactoring: The software behavior remains unchanged after the code change. These changes are made for imporving codebase's maintainability, better readability or encapsulation.
\end{itemize}
